Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective \titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2015-04-30 thesis/acm/paper.tex
Removed a note
Removed a note that was mistakenly left in place
law 7

%%Describe the change 
Adds functionality which allows to connect with other hardware through serial communication
Allows the possibility to integrate other systems with the camera (such as a ticket dispenser (i guess))

The final new feature of the API was the inclusion of axserialport. This part of the API allows API users to connect various devices to their cameras through the use of a serial port. This effectively allows users to integrate multiple kinds of devices to create their own unique solutions. In the previous version of the API there was no ability to connect to devices outside of the VMS.

@@

\subsubsection{3\textsuperscript{rd} Party}
ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)

@@

\subsection{Increasing Complexity}
A large part of the changes made to the API were made to improve the structure and the way that the API is used. Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API. One example of this is the change to the interfaces which set a standard for the whole API. During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs. It was also made clear a contributing factor for changing certain parts of the API was to bring it in line with the new interfaces. The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these. Even though the importance of maintaining the API to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented. One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream. It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyways (!!!reword). Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.

@@

\subsection{Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
Updates to documentation
Updates to interfaces and error handling

It's not 100\% true for APIs, because updating it too often will cause other problems --> ``rigorously''

\subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
She would like to get more feedback from the API users and the end-users - to better include this in the feedback loop and in turn use it to form change decisions

>>>>

%%Describe the change 
The final new feature of the API was the inclusion of axserialport. This part of the API allows API users to connect various devices to their cameras through the use of a serial port. This effectively allows users to integrate multiple kinds of devices to create their own unique solutions. In the previous version of the API there was no ability to connect to devices outside of the VMS.

@@

\subsubsection{3\textsuperscript{rd} Party}y e
ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)

@@

\subsection{Increasing Complexity} \label{law2}
A large part of the changes made to the API were made to improve the structure and the way that the API is used. Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API. One example of this is the change to the interfaces which set a standard for the whole API. During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs. It was also made clear a contributing factor for changing certain parts of the API was to bring it in line with the new interfaces. The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these. Even though the importance of maintaining the API to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented. One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream. It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyways (!!!reword). Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.

@@

\subsection{Declining Quality}
The interviews established that a groomative motive was not the most major reason for implementing any change. The changes to the example code and the SDK, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content. These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out. A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{law2}. We therefore settle that the law of declining quality can be applied to APIs.

\subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
One of the 
She would like to get more feedback from the API users and the end-users - to better include this in the feedback loop and in turn use it to form change decisions
